Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-13 paper/paper.tex
update

>>>>

Anglican programs are executed by inference algorithms, which
compute approximate answers to certain probabilistic queries, such as posterior
inference and marginal likelihood. This execution 
is significantly different from that of usual programs. For instance, 
inference algorithms typically run Anglican programs multiple times, 
often hundreds of thousands or even millions of times for a single inference
task. Also, they make random choices, some of which do not even appear in the program
explicitly, and these choices may affect which parts of the program code
are executed and how often. Some inference algorithms 
re-run the program multiple times partially, from a certain
point on, while reusing random choices made in the previous runs as much as possible. 
In a sense, each inference algorithm is nothing but a virtual machine for Anglican that
executes Anglican programs according to a non-standard operational semantics. Supporting 
a wide range of non-standard semantics of inference algorithms is the main reason that we
developed Anglican as a language rather than as a library.

\hy{I am here.}
